Clustering Beat-Chroma Patterns in a Large Music Database

### 2010-03-23 Paper/Paper.tex
good day sunshine added
improved caption for experiment where we square codebook size

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.99\columnwidth]{data_sizes}
\end{center}
\caption{\small{Distortion for a codebook of size $100$ encoding one bar
at a time, a bar being represented by $4$ chroma feature vector.
Therefore, a code or a pattern is of size $12$ x $4$ = $48$.
Distortion measure on the test data set. Data size tested range
from $10$ thousands to $2$ millions. Patterns were selected at
random from the dataset of approximately $3,7$ million patterns.
OLD GRAPH WITH OLD NUMBERS
}}
\label{fig:data_sizes}
\end{figure}

@@

% see generate_expo_codes_curves.py to generate the following figure:
\begin{figure}[htb]
\begin{center}
\includegraphics[width=.99\columnwidth]{codesize_patternsize}
\end{center}
\caption{\small{NEW RESULTS COMING IN}}
\label{fig:size_pattern}
\end{figure}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.9\columnwidth]{song_encoded}
\end{center}
\caption{\small{Original song and its encoding. Must get a better one for
the paper!!!!!!  What happened to good day sunshine?}}
\label{fig:encodesong}
\end{figure}

>>>>

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.99\columnwidth]{data_sizes}
\end{center}
\caption{\small{Distortion for a codebook of size $100$ encoding one bar
at a time, a bar being represented by $4$ chroma feature vector.
Therefore, a code or a pattern is of size $12$ x $4$ = $48$.
Distortion measure on the test data set. Data size tested range
from $0$ (just initialization) to $500$ thousand. Patterns were selected at
random from the dataset of approximately $3,7$ million patterns, except
for the dotted line (non random in the legend). In that case we took the
first $N$ samples in our dataset. The difference is only visible for small
training sets ($1$K).
}}
\label{fig:data_sizes}
\end{figure}

@@

% see generate_expo_codes_curves.py to generate the following figure:
\begin{figure}[htb]
\begin{center}
\includegraphics[width=.99\columnwidth]{codesize_patternsize}
\end{center}
\caption{\small{
Experiment on squaring the codebook size when the pattern size doubles.
Each line represent $4$ codebook sizes: $2$, $4$, $16$ and $256$.
The pattern size range from $1$ for $1/4$ of a bar to $32$ for $8$ bars.
If everything was random, each of these lines should be flat.
}}
\label{fig:size_pattern}
\end{figure}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.9\columnwidth]{song_encoded}
\end{center}
\caption{\small{Good Day Sunshine by \textit{The Beatles}.
Original song and its encoding using a $200$ codes codebook learning
$2$ bars at a time.
}}
\label{fig:encodesong}
\end{figure}
